---
title: "MixSwitchEpi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MixSwitchEpi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MixSwitchEpi)
library(cli)
library(ggplot2)
message("loaded MixSwitchEpi")
```

MixSwitchEpi provides a simple model for parameterically varying patterns of interpersonal contact ('Mix'), and changes include contact
patterns through time ('switch'). It allows us to explore the effect of these changes on epidemic dynamics ('Epi'). 

The package provides tools to define and simulate compartmental epidemic models with varying contact patterns, using odin2 and dust2 for efficient simulation. 

# A simple simulation

We illustrate the central principles of the package using a simple simulated epidemic in a population. 

It will be useful for our analysis to retrieve some 

```{r}
library(epiparameter)

epiparameters <- epiparameter_db()

influenza_incubation <- epiparameter_db(
  disease = "influenza",
  epi_name = "incubation period",
  single_epiparameter = TRUE
)

covid_params <- epiparameter_db(
  disease = "COVID-19",
  epi_name = "incubation period", single_epiparameter = T
)
```

First let's definine a basic set of parameters with switching `parms_wswitch`, using the convenience function `default_setup()`.
```{r, echo=F}
# parms_wswitch <- MixSwitchEpi::default_setup()
```


To illustrate the method, we have chosen a switching rate of 0.25. This corresponds to there being a 

These baseline parms will be the 

## Defining contact patterns

Subdivide the population into 5 activity classes. In the most general case, the activity classes represent the number of risky
exposures per unit time. Clearly, this is 




## Performing the static approximations


#### Constrained approximation: 

```{r}
main_demo <- function(n_activity,
                      switch_rate,
                      initial_condition_rule,
                      pathogen_string,
                      activity_scheme) {
  parms <- make_parms(
    n_activity = n_activity,
    switch_rate = switch_rate,
    initial_condition_rule = initial_condition_rule,
    pathogen_string = pathogen_string, activity_scheme = activity_scheme
  )
  model <- seirs_act()

  reference <- MixSwitchEpi::run_system_wparms(parms = parms, model = model)

  fit_res <- MixSwitchEpi::fit_noswitch(parms, model)
  approx_parms <- fit_res$best_parms

  cat(sprintf(
    "Best epsilon: %0.4f (cost=%0.6g)\n",
    fit_res$best_eps, fit_res$best_cost
  ))

  approx_sim <- MixSwitchEpi::run_system_wparms(
    parms = approx_parms,
    model = model
  )

  Ntot <- parms$N
  print(reference)
  df_ref <- data.frame(time = reference$time, i = reference$i_tot / Ntot, type = "reference")
  df_approx <- data.frame(time = approx_sim$time, i = approx_sim$i_tot / Ntot, type = "approximation")
  df_plot <- rbind(df_ref, df_approx)

  p <- ggplot(df_plot, aes(x = time, y = i, color = type)) +
    ggplot2::geom_line() +
    ggplot2::theme_minimal() +
    ggplot2::labs(
      title = "Reference system and no-switch approximation",
      x = "Time", y = "Prevalence (I / N)"
    ) +
    ggplot2::scale_color_manual(values = c("reference" = "#1f78b4", "approximation" = "#e31a1c"))

  ggplot2::ggsave(filename = "noswitch_approx.svg", plot = p, width = 9, height = 4)
}
```


```{r}
# main_demo(switch_rate = 0.25,
#           n_activity = 5,
#           initial_condition_rule = "uniform",
#           pathogen_string = "sars-cov-2" )
```

### Unconstrained approximation

Here we relax the constraint that the contact pattern must be generated by the Garnett model. 


# ::: {#refs}
:::


