---
title: "Comparing Homogeneous and Heterogeneous Epidemics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparing Homogeneous and Heterogeneous Epidemics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This file contains methods used for comparing the 
    1. homogeneous population case (i.e. no activity differences) and
    2. the heterogeneous population case, epsilon = 0 (i.e. with activity differences but proportionate mixing). 
    3. heterogeneous case with epsilon = 0.5 (i.e. with activity differences and some assortativity).
    4. as (3) but with some switching between activity classes.

This is intended to illustrate to the reader the effect of heterogeneity and activity switching on the epidemic dynamics.
```{r}
library(MixSwitchEpi)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(tidyr)
```

```{r}
# set up parameters for the comparison
N <- 1e6
n_activity <- 5
R0 <- 2.5
homogeneous_case <- scalar_reference(R0)

# for the heterogeneous case we require the activity scores, which we get from the empirical data
activity_scores <- activity_empirical("haslemere", n_activity)

source("/Users/alexis/Documents/sph_imperial/MixSwitchEpi/scripts/run_compare_curves.R")